---
title: "PH1976 Project: Predicting Parkinson’s Disease for Patients Using Voice Recording"
author: "Erin S. King, Name, Name, Name, Name"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    fig_caption: TRUE
    citation_package: biblatex
    biblio-style: apa
    split_bib: false
bibliograpy: packages.bib
---
```{r, include=FALSE}
#Set the working directory and get the data
project_dir = dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(project_dir)
training_set_path = paste(project_dir,'/Project data_2023_p 2/Project data_2023_p/project_training set_p.csv',sep="")
test_set_path = paste(project_dir,'/Project data_2023_p 2/Project data_2023_p/project_test set_p.csv',sep="")
training_data = read.csv(training_set_path)
test_data = read.csv(test_set_path)

# Grab packages if not installed
# Note, if RStudio is having issues w/ tidyverse, run this command in R (not Rstudio):
# install.packages("https://cran.r-project.org/src/contrib/rlang_1.1.0.tar.gz", repos = NULL, type="source")
list.of.packages <- c("tidyverse", "broom", "mosaic","ggplot2", "bookdown", "Boruta","mlbench","caret","randomForest", "neuralnet","e1071","kernlab","naivebayes", "class", "caretEnsemble")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
for(package in list.of.packages){
  require(package, character.only = TRUE)
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::write_bib(list.of.packages, "packages.bib",width = 60)
```

# Introduction
The following analysis in this PH1976 project is to demonstrate the tools examined in this course for data categorization, regression, and prediction. The project's aim is to predict Parkinson’s disease (PD) using the extracted features from the voice recording of patients. For each individual, three recording samples were collected. The [data and corresponding analysis](https://doi.org/10.1016/j.asoc.2018.10.022) is provided by @Sakar in their seminal research on implementing tunable Q-factor wavelet transforms in conjunction with existing data prediction methods. The methods found in this study serve as a roadmap for this project and inform the methods chosen for categorization and prediction.  

## Definition
Parkinson’s disease (PD) is a progressive neurodegenerative disorder. To accurately detect the disease in the
early stage, many telediagnosis and telemonitoring systems have recently been proposed. Since vocal problem is
one of the most important symptoms which can be seen in the earlier stage of PD patients, vocal disorders-
based systems become popular in PD diagnosis and monitoring. In these systems, various speech signal
processing algorithms have been used to extract clinically useful information for PD assessment, and the
calculated features are fed to different learning algorithms to make reliable decisions. PD telemedicine studies
showed that the choice of extracted features and learning algorithms directly influences the accuracy and
reliability of distinguishing PD patients.  

## Data
In this study, Sakar et. al collected the voice recordings of 252 subjects including PD patients and healthy individuals. They gathered three recording samples from each subject and extracted seven feature subsets from the recording samples. The feature subsets were baseline features, intensity-based features, bandwidth and formant features, vocal fold features, Mel Frequency Cepstral Coefficients (MFCC), wavelet transform based features (WT) and tunable Q-factor wavelet transform based features (TQWT).  

## Study Design
Need to fill this out based on our own analysis.  

## Study Population
The dataset includes PD patients with age ranging from 33 to 87 (65.1 ± 10.9) and healthy individuals with age
ranging from 41 to 82 (61.1 ± 8.9). Each patient has three voice recording samples, with 7 aforementioned
feature subsets. Each feature subset contains several features.  

# Dataset
## Preprocessing and Standardization  
Instead of using the LOOCV method outlined in the paper, we have decided to break the training dataset into a 90/10 split, where 90% of the data will be used to train, and 10% of the data will be used to check accuracy of the model. The best model for each subset will be selected based on these results.  

```{r,include=FALSE}
# Load caret package if not already loaded
if (!"caret" %in% rownames(installed.packages())) {
  install.packages("caret")
}
library(caret)

# Set seed for reproducibility
set.seed(123)

#Break the training data into feature subsets
train_df.baseline = data.frame(training_data[c(1:24)])
train_df.intensity = data.frame(training_data[c(1:3,25:27)])
train_df.formant = data.frame(training_data[c(1:3,28:35)])
train_df.vff = data.frame(training_data[c(1:3,36:57)])
train_df.mfcc = data.frame(training_data[c(1:3,58:141)])
train_df.wt = data.frame(training_data[c(1:3,142:323)])
train_df.tqwt = data.frame(training_data[c(1:3,324:755)])

#Partition training data
train_indices <- createDataPartition(train_df.baseline$class, p = 0.9, list = FALSE)

# Split train_df data
train_df.baseline_train <- train_df.baseline[train_indices, ]
train_df.baseline_test <- train_df.baseline[-train_indices, ]

train_df.intensity_train <- train_df.intensity[train_indices, ]
train_df.intensity_test <- train_df.intensity[-train_indices, ]

train_df.formant_train <- train_df.formant[train_indices, ]
train_df.formant_test <- train_df.formant[-train_indices, ]

train_df.vff_train <- train_df.vff[train_indices, ]
train_df.vff_test <- train_df.vff[-train_indices, ]

train_df.mfcc_train <- train_df.mfcc[train_indices, ]
train_df.mfcc_test <- train_df.mfcc[-train_indices, ]

train_df.wt_train <- train_df.wt[train_indices, ]
train_df.wt_test <- train_df.wt[-train_indices, ]

train_df.tqwt_train <- train_df.tqwt[train_indices, ]
train_df.tqwt_test <- train_df.tqwt[-train_indices, ]
```
For ease of analysis, the ensemble data set (both training and test) are broken into the following sub feature categories:  

* Baseline Features
* Time Frequency Features 
    + Intensity based
    + Formant and Bandwidth based
* Vocal Fold Features
* Mel Frequency Cepstral Coefficients (MFCC)
* Wavelet Transform-based Features
* Tunable Q-Factor Wavelet Transform-based Features (TQWT)  

```{r, include=FALSE}

# Standardizing the data for cross-comparison

require(tidyverse)
require(broom)
require(mosaic)

# Standardizing the data for cross-comparison
# Training and Test Data
subset_names <- c("baseline", "intensity", "formant", "vff", "mfcc", "wt", "tqwt")

# Standardize function
standardize_data <- function(train_df, test_df) {
  for (ii in 4:length(train_df)) {
    mean_val <- mean(train_df[, ii], na.rm = TRUE)
    std_val <- sd(train_df[, ii], na.rm = TRUE)
    
    train_df[, ii] <- (train_df[, ii] - mean_val) / std_val
    
    if (!is.null(test_df)) {
      test_df[, ii] <- (test_df[, ii] - mean_val) / std_val
    }
  }
  return(list(train_df, test_df))
}

# Standardize train and test datasets
for (i in subset_names) {
  # Standardize train_df and test_df
  standardized_data <- standardize_data(get(paste0("train_df.", i, "_train")), get(paste0("train_df.", i, "_test")))
  assign(paste0("train_df_std.", i, "_train"), standardized_data[[1]])
  assign(paste0("train_df_std.", i, "_test"), standardized_data[[2]])
}

# Standardize test dataset
  standardized_data <- standardize_data(get(paste0("training_data")), get(paste0("test_data")))
  assign(paste0("test_df_std"), standardized_data[[2]])

```

To start, data from all sub features are standardized such that each feature has zero mean and unit variance. This was accomplished using the [@tidyverse], [@broom], and [@mosaic] packages in RStudio. The histograms below shows an example transformation of the original training data set to the standardized form from the **Baseline**, **Intensity**, and **Formant** sub features. This allows all data comparisons to be made equivalently. To ensure that training and test data are all benchmarked equivalently, mean and standard deviation is calculated using the training data, and is applied to standardize both the training and test data. This way, no information leakage will occur and the models will be provided standardized data that is unbiased.  

```{r, include = FALSE}

plot_subfeatures <- function(subfeature_name, train_df, train_df_std) {
  optimal_mfrow <- function(num_plots) {
    max_cols <- floor(sqrt(num_plots))
    num_rows <- ceiling(num_plots / max_cols)
    return(c(num_rows, max_cols))
  }

  num_plots <- ncol(train_df) - 2

  # Pre-standardization
  cat(paste0("\\begin{figure}[h]\\centering\n"))
  cat(paste0("\\caption{", subfeature_name, " Sub-feature: Pre-standardization}\n"))

  par(mfrow = optimal_mfrow(num_plots))
  for (ii in 3:ncol(train_df)) {
    hist(train_df[, ii], main = "", xlab = colnames(train_df)[ii])
  }
  cat("\\end{figure}\n")

  # Post-standardization
  cat(paste0("\\begin{figure}[h]\\centering\n"))
  cat(paste0("\\caption{", subfeature_name, " Sub-feature: Post-standardization}\n"))

  par(mfrow = optimal_mfrow(num_plots))
  for (ii in 3:ncol(train_df_std)) {
    hist(train_df_std[, ii], main = "", xlab = colnames(train_df_std)[ii])
  }
  cat("\\end{figure}\n")
}


```

```{r, echo=FALSE, results='asis', fig.width=10, fig.height=10}

selected_subsets <- c("baseline", "intensity", "formant")
# Generate plots using function
for (selected_subset in selected_subsets) {
  train_df_subset <- get(paste0("train_df.", selected_subset, "_train"))
  train_df_std_subset <- get(paste0("train_df_std.", selected_subset, "_train"))
  
  plot_subfeatures(selected_subset, train_df_subset, train_df_std_subset)
}
```
  
## Feature Selection
Per the **Sakar et al** paper, minimum redundancy-maximum relevance based filter feature selection methods are ideal for determining effective features. The advantage of this is two-fold:
1. It reduces the high dimensionality of the data set.
2. It maximizes the joint dependency of the data set.
This strategy is used frequenty in machine learning and regression applications, and as such, will be used in this analysis. The **Boruta** package in RStudio will be used for this purpose, and utilizes Random Forest to perform a top-down search on the corresponding data frame to determine relevant features.     



```{r boruta, include = FALSE}
require(Boruta)
require(mlbench)
require(caret)
require(randomForest)
# Function to perform Boruta feature selection
perform_boruta <- function(dataset_name, standardized_train_df, max_runs = 500) {
  cat("Performing Boruta on", dataset_name, "\n")
  set.seed(123)
  boruta_result <- Boruta(class ~ ., data = standardized_train_df, doTrace = 2, maxRuns = max_runs)
  return(boruta_result)
}

# Call the perform_boruta function for each subset. Finds important features in each subset
boruta_results <- list()
for (subset_name in subset_names) {
  standardized_train_df <- get(paste0("train_df_std.", subset_name, "_train"))
  boruta_result <- perform_boruta(subset_name, standardized_train_df)
  boruta_results[[subset_name]] <- boruta_result
}
```

```{r, include=FALSE}
# Boruta plot function for multiple objects
generate_boruta_plots <- function(boruta_list) {
  for (name in names(boruta_list)) {
    label <- paste0("Boruta plot for ", name, " features")
    fig_label <- paste0("fig:", gsub(" ", "_", tolower(label)))
    
    cat(paste0("\\begin{figure}[ht!]\n"))
    cat(paste0("\\centering\n"))
    cat(paste0("\\caption{", label, "}\n"))
    cat(paste0("\\label{", fig_label, "}\n"))
    
    plot(boruta_list[[name]], las = 2, main = paste0(name, " mRMR"))
    
    cat("\\end{figure}\n")
  }
}

```
mRMR analysis yields the following results:  
```{r, echo=FALSE}
# Generate Boruta plots using the generate_boruta_plots function
generate_boruta_plots(boruta_results)

```
  
Following this initial assessment, chosen variables are selected for regression by using **getNonRejectedFormula()**. This collapses any variables left as **Tentative** factors into either 
```{r, include=FALSE}
#Force "Tentative" values function
get_chosen_features <- function(boruta_results) {
  chosen_features <- list()
  for (name in names(boruta_results)) {
    chosen_formula <- getNonRejectedFormula(TentativeRoughFix(boruta_results[[name]]))
    chosen_features[[name]] <- chosen_formula
  }
  return(chosen_features)
}
```

``````{r, echo=FALSE}
# Get chosen features using the get_chosen_features function
chosen_features <- get_chosen_features(boruta_results)
```

## Model Selection
```{r, include = FALSE}

#Function for Multilayer Perceptron
train_mlp <- function(train_df, formula) {
  library(neuralnet)
  set.seed(123)
  
  threshold_func <- function(x) ifelse(x > 0.5, 1, 0)
  train_df$class <- as.numeric(train_df$class) - 1
  
  mlp_model <- neuralnet(formula, data = train_df, hidden = c(5), linear.output = FALSE, act.fct = "logistic", stepmax = 1e+05)
  return(list(model = mlp_model, threshold_func = threshold_func))
}

test_model <- function(model_obj, test_df, model_type, chosen_formula) {
  if (model_type == "mlp") {
    model <- model_obj$model
    threshold_func <- model_obj$threshold_func
    
    test_data <- model.matrix(chosen_formula, data = test_df)[, -1]
    predictions <- compute(model, test_data)$net.result
    predicted_classes <- sapply(predictions, threshold_func)
    actual_classes <- test_df$class
    
    accuracy <- sum(predicted_classes == actual_classes) / length(actual_classes)
  } else {
    predictions <- predict(model_obj, test_df)
    
    if (model_type %in% c("logit", "svm_linear", "svm_rbf")) {
      predicted_classes <- ifelse(predictions > 0.5, 1, 0)
    } else {
      predicted_classes <- predictions
    }
    actual_classes <- test_df$class
    
    accuracy <- sum(predicted_classes == actual_classes) / length(actual_classes)
  }
  
  return(accuracy)
}

```


```{r, include = FALSE}

#Modeling function
generate_models <- function(dataset_name, train_df, test_df) {
  library(caret)
  library(randomForest)
  library(e1071)
  library(nnet)
  library(kernlab)
  library(naivebayes)
  
  set.seed(123)
  # Create chosen_formula
  chosen_formula <- as.formula(chosen_features[[dataset_name]])

  # Convert the class variable into a factor
  train_df$class <- as.factor(train_df$class)
  test_df$class <- as.factor(test_df$class)

  # Create chosen_formula
  chosen_formula <- as.formula(chosen_features[[dataset_name]])

  # Train/test data
  train_data <- model.matrix(chosen_formula, data = train_df)[, -1]
  train_class <- train_df$class
  test_data <- model.matrix(chosen_formula, data = test_df)[, -1]
  test_class <- test_df$class

  # Initialize list to store models and accuracy
  models_and_accuracy <- list()

  # Logistic Regression
  logit_model <- glm(formula = chosen_formula, family = "binomial", data = train_df)
  logit_predictions <- predict(logit_model, newdata = test_df, type = "response")
  logit_predicted_classes <- ifelse(logit_predictions > 0.5, 1, 0)
  accuracy_logit <- sum(logit_predicted_classes == test_class) / length(test_class)

  models_and_accuracy[["Logistic\nRegression"]] <- list(model = logit_model, accuracy = accuracy_logit)
  
  # Define the parameter grid for tuning the Random Forest
  tuneGrid <- expand.grid(mtry = sqrt(ncol(train_df)),
                        splitrule = "gini",
                        min.node.size = c(1, 3, 5, 10, 15))

  # Set up cross-validation
  cvControl <- trainControl(method = "cv", number = 5, search = "grid")

  # Random Forest model using cross-validation
  rf_model <- train(chosen_formula, data = train_df,
                  method = "ranger",
                  trControl = cvControl,
                  tuneGrid = tuneGrid,
                  importance = "none",
                  num.trees = 500)
  
  rf_pred <- predict(rf_model, newdata = test_df)
  accuracy_rf <- sum(rf_pred == test_class) / length(test_class)

  models_and_accuracy[["Random\nForest"]] <- list(model = rf_model, accuracy = accuracy_rf)

  # SVM with Linear Kernel
  svm_linear <- svm(train_data, train_class, kernel = "linear")
  predictions_linear <- predict(svm_linear, test_data)
  accuracy_linear <- sum(predictions_linear == test_class) / length(test_class)

  models_and_accuracy[["SVM\nLinear"]] <- list(model = svm_linear, accuracy = accuracy_linear)

  # SVM with RBF Kernel
  svm_rbf <- svm(train_data, train_class, kernel = "radial")
  predictions_rbf <- predict(svm_rbf, test_data)
  accuracy_rbf <- sum(predictions_rbf == test_class) / length(test_class)

  models_and_accuracy[["SVM RBF"]] <- list(model = svm_rbf, accuracy = accuracy_rbf)

  # Multilayer Perceptron
  mlp_model <- train_mlp(train_df, chosen_formula)
  accuracy_mlp <- test_model(mlp_model, test_df, "mlp", chosen_formula)

  models_and_accuracy[["Multilayer\nPerceptron"]] <- list(model = mlp_model$model, accuracy = accuracy_mlp)

  # Naive Bayes
  nb_model <- naive_bayes(chosen_formula, data = train_df)
  nb_predictions <- predict(nb_model, newdata = test_df)
  accuracy_nb <- sum(nb_predictions == test_class) / length(test_class)

  models_and_accuracy[["Naive\nBayes"]] <- list(model = nb_model, accuracy = accuracy_nb)

  # KNN
  k <- 10
  knn_predictions <- knn(train = train_data, test = test_data, cl = train_class, k = k)
  accuracy_knn <- sum(knn_predictions == test_class) / length(test_class)
  knn_model <- list(train_data = train_data, train_class = train_class, k = k)

  models_and_accuracy[["KNN"]] <- list(model = knn_model, accuracy = accuracy_knn)

  # Generate a bar plot comparing the accuracy of each model
  model_names <- names(models_and_accuracy)
  model_accuracies <- sapply(models_and_accuracy, function(x) x$accuracy)

  plot_title <- paste0("Model Accuracies for ", dataset_name)
  par(mar = c(8, 4, 4, 2) + 0.1)  # Increase bottom margin size
  barplot(model_accuracies, names.arg = model_names, main = plot_title, xlab = "Models", ylab = "Accuracy", las = 2)
  par(mar = c(5, 4, 4, 2) + 0.1)  # Reset the margins to default values

  return(models_and_accuracy)
}

```

```{r, echo = FALSE}

#Pass chosen_features, subset_names, and training/test data to choose the best model.
best_models <- list()

for (subset_name in subset_names) {
  train_df <- get(paste0("train_df_std.", subset_name, "_train"))
  test_df <- get(paste0("train_df_std.", subset_name, "_test"))

  models_and_accuracy <- suppressWarnings(generate_models(subset_name, train_df, test_df))

  # Find the model with the highest accuracy
  best_model <- names(which.max(sapply(models_and_accuracy, function(x) x$accuracy)))
  cat("Best model for", subset_name, "is", best_model, "with an accuracy of", models_and_accuracy[[best_model]]$accuracy, "\n")

  # Store the best model for this subset
  best_models[[subset_name]] <- list(model = models_and_accuracy[[best_model]]$model, accuracy = models_and_accuracy[[best_model]]$accuracy)
}

```

```{r, echo=FALSE}

train_ensemble_model <- function(train_df) {
  control <- trainControl(method = "repeatedcv", number = 10, repeats = 3, savePredictions = "final", classProbs = TRUE)
  metric <- "Accuracy"

  # Define the list of models for the ensemble
  model_list <- c("glm", "svmLinear", "svmRadial", "nnet", "naive_bayes", "ranger", "knn")

  # Train the ensemble model using stacking and caretList
  ensemble_model <- caretList(formula = chosen_formula, data = train_df, methodList = model_list, trControl = control, metric = metric)
  
  return(ensemble_model)
}

```

```{r, echo+FALSE}

evaluate_ensemble_model <- function(ensemble_model, test_df) {
  # Make predictions with the ensemble model
  predictions <- predict(ensemble_model, newdata = test_df)

  # Calculate accuracy
  test_class <- test_df$class
  accuracy <- sum(predictions == test_class) / length(test_class)
  
  return(accuracy)
}

```

```{r, echo=FALSE}

ensemble_prediction <- function(train_df, test_df, new_data) {
  # Train the ensemble model
  ensemble_model <- train_ensemble_model(train_df)
  
  # Evaluate the ensemble model
  accuracy <- evaluate_ensemble_model(ensemble_model, test_df)
  cat("Ensemble model accuracy:", accuracy, "\n")
  
  # Make predictions for the new data
  predictions <- predict(ensemble_model, newdata = new_data)
  
  # Overwrite the Class column in the new_data dataset with the predictions
  new_data$class <- predictions
  
  return(new_data)[1:2,]
}

```

```{r, echo=FALSE}

library(randomForest)
library(e1071)
library(nnet)
library(kernlab)
library(naivebayes)
library(dplyr)
library(caretEnsemble)

# Combine the training and test datasets of each subfeature and add unique ID
combined_train_df <- Reduce(function(x, y) left_join(x, y, by = "id"), lapply(subset_names, function(subset_name) {
  df <- get(paste0("train_df_std.", subset_name, "_train"))
  df$id <- seq_len(nrow(df))
  df
}))

combined_test_df <- Reduce(function(x, y) left_join(x, y, by = "id"), lapply(subset_names, function(subset_name) {
  df <- get(paste0("train_df_std.", subset_name, "_test"))
  df$id <- seq_len(nrow(df))
  df
}))

# Create chosen_formula
chosen_columns <- setdiff(names(combined_train_df), c("class", "id"))
terms_rhs <- paste(chosen_columns, collapse = " + ")
terms_lhs <- quote(class)
terms_env <- as.environment(as.list(terms_lhs))
eval(parse(text = paste("terms_lhs <- class ~", terms_rhs)), envir = terms_env)
chosen_formula <- as.formula(terms_lhs, env = terms_env)

# Train and evaluate the ensemble model using the combined train and test datasets
predictions <- ensemble_prediction(combined_train_df, combined_test_df, test_df_std)

# Print predictions
print(predictions)
```